\section{Project Summary and Team Evaluation}
\label{sec:team_evaluation}

This final section provides a comprehensive overview of the project's management, the team's collaborative process, and an evaluation of the overall workflow from inception to completion.

\subsection{Member Contributions and Task Allocation}
The project's success was built on a clear allocation of tasks and the dedicated contribution of each team member. The work was divided based on individual strengths and interests to maximize efficiency and quality.

\begin{center}
	\begin{table}[H]
		\renewcommand{\arraystretch}{1.5}
		\setlength{\tabcolsep}{8pt}
		% Lưu ý: \rowcolors không hiển thị đẹp với \multirow, nên tạm thời không dùng cho bảng này

		% Sử dụng tabularx và thay đổi cột cuối thành 'c' (center) cho phù hợp
		\begin{tabularx}{\textwidth}{| c | l | X |}
			\hline
			\rowcolor{gray!30}
			\textbf{Name} & \textbf{Contribution}       & \textbf{Detail}                                       \\
			\hline

			% Du Hoai Phuc - Team Leader & Core Architecture
			\multirow{7}{*}{\parbox{3.5cm}{\centering\textbf{Du Hoai Phuc}                                      \\ \small{(Team Leader \& Core Architecture)}}}
			              & Core Classes Design         & User, Member, Librarian, Book, Author, Category, Loan \\
			\cline{2-3}
			              & Polymorphism Implementation & Virtual functions, runtime behavior selection         \\
			\cline{2-3}
			              & Project Coordination        & Timeline management, code integration                 \\
			\cline{2-3}
			              & Design Patterns Architect   & Observer, Strategy, Decorator patterns                \\
			\cline{2-3}
			              & User Experience Design      & System workflow and interaction design                \\
			\hline

			% Ly Huynh Minh Dang - Backend Systems Developer
			\multirow{8}{*}{\parbox{3.5cm}{\centering\textbf{Ly Huynh Minh Dang}                                \\ \small{(Backend Systems Developer)}}}
			              & Data Persistence            & CSV-based storage with CSVHandler utility             \\
			\cline{2-3}
			              & Library Management Services & LibraryManager singleton implementation               \\
			\cline{2-3}
			              & Loan Management             & Borrowing/returning system with fine calculation      \\
			\cline{2-3}
			              & Business Logic              & Core operations and member status management          \\
			\cline{2-3}
			              & Input Validation            & Form validation and error handling                    \\
			\hline

			% Ta Duc Dung - UI/UX Developer
			\multirow{5}{*}{\parbox{3.5cm}{\centering\textbf{Ta Duc Dung}                                       \\ \small{(UI/UX Developer)}}}
			              & GUI Implementation          & Complete ImGui-based interface                        \\
			\cline{2-3}
			              & Authentication System       & Login/logout with password validation                 \\
			\cline{2-3}
			              & Visual Design               & Consistent styling and layout                         \\
			\cline{2-3}
			              & Responsive Interface        & Smooth navigation and interaction                     \\
			\cline{2-3}
			              & User Experience Design      & Intuitive menu systems                                \\
			\hline
		\end{tabularx}
		\caption{Individual Contributions}
	\end{table}
\end{center}

\newpage

\begin{center}
	\begin{table}[H]
		\renewcommand{\arraystretch}{1.5}
		\setlength{\tabcolsep}{8pt}
		% Lưu ý: \rowcolors không hiển thị đẹp với \multirow, nên tạm thời không dùng cho bảng này

		% Sử dụng tabularx và thay đổi cột cuối thành 'c' (center) cho phù hợp
		\begin{tabularx}{\textwidth}{| c | l | X |}
			\hline
			\rowcolor{gray!30}
			\textbf{Name} & \textbf{Contribution}       & \textbf{Detail}                                       \\
			\hline

			% Nguyen Son Hai - Designer & Tester
			\multirow{5}{*}{\parbox{3.5cm}{\centering\textbf{Nguyen Son Hai}                                    \\ \small{(Designer \& Tester)}}}
			              & Slide Maker                 & Presentation materials and diagrams                   \\
			\cline{2-3}
			              & Report Writing              & Technical documentation                               \\
			\cline{2-3}
			 & Encapsulation Implementation & Data validation and access control \\
			\cline{2-3}
			 & Inheritance Hierarchy & User base class with derived classes \\
			\cline{2-3}
			              & Tester                      & System testing and quality assurance                  \\
			\hline
		\end{tabularx}
		\caption{Individual Contributions}
	\end{table}
\end{center}

\subsection{Development Workflow and Collaboration}
To ensure a smooth and organized development process, our team adopted a structured workflow utilizing industry-standard tools and practices.

\begin{itemize}
	\item \textbf{Version Control:} All source code was managed using \textbf{Git}, a distributed version control system that is the de facto standard in modern software development \cite{Chacon2014}. A central repository was hosted on \textbf{GitHub}, and the team followed a feature-branch workflow to facilitate parallel development and code review before integration.

	\item \textbf{Communication:} Primary communication was conducted through a dedicated \textbf{Discord} channel for daily updates and quick questions. We also held weekly online meetings to discuss progress, resolve blocking issues, and plan the next steps.

	\item \textbf{Task Management:} We utilized a simple Kanban-style board on \textbf{Trello} to track the status of all tasks (To Do, In Progress, Done). This provided clear visibility into the project's overall progress and helped identify bottlenecks early.
\end{itemize}

\subsection{Key Challenges and Resolutions}
Throughout the project, we encountered several challenges that tested our problem-solving and teamwork skills:

\begin{description}
	\item[Technical Design Decisions]
	      \textbf{Challenge:} Choosing the most suitable design patterns from the catalog presented by Gamma et al. \cite{GoF1994} was a point of extensive debate.
	      \textbf{Resolution:} The team held dedicated design sessions where we would whiteboard different approaches and discuss the pros and cons of each. The final decision was always made collectively to ensure everyone understood the chosen architecture.

	\item[Code Integration]
	      \textbf{Challenge:} As members completed their features, merging different Git branches occasionally resulted in code conflicts.
	      \textbf{Resolution:} We resolved this by adopting a policy of frequent communication. Before starting a major change, members would announce their plans to the team. Before merging, the developer would pull the latest changes from the main branch to resolve conflicts locally first.

	\item[Data Integrity Verification]
	      \textbf{Challenge:} Ensuring the integrity of data stored in plain text CSV files was a significant security concern.
	      \textbf{Resolution:} We implemented a mechanism to compute and store a cryptographic hash (using SHA-256) for each data file. Before reading any file, the system re-computes its hash and compares it to the stored value to detect any tampering, a fundamental technique in data security \cite{Stallings2017}.
\end{description}